---
title: "Homework 2"
author: "Justine"
date: "October 19, 2015"
output: html_document
---
#PART 1

##2.2
###a.
The proportion of patients in the treatment group who have died is 0.65. The proprotion of patients in the control group who have died is 0.88.
###b.
####i.
H0: Transplants have no effect on patient survial. pt - pc = 0.
HA: Transplants have an impact on survival. pt- pc does not equal 0.
####ii.
28, 75, 69, 34, 0, -0.23.
####iii. 
The point estimate is not included in the simulated difference in proportions. It seems to suggest that we reject the null hypothesis and the treatment is effective.

##3.28.
p1 hat = 0.088
p2 hat = 0.08
point estimate: p1 hat - p2 hat = 0.008
Z =1.96 (95% confidence interval)
SE = 0.00485
95% confident that the difference of porportion of Califonians and Oregonians who are sleep deprived is between 0.15% and 1.7%.

##3.30.
###a.
H0: Sleep deprevation is not effected by living in different states
HA: Sleep deperation is different within Oregan and California
check conditons: Random samples, independent and normally distriubted. Also each group is independent. Therefore we can use the T-Test.
point estimate = 0.0823
null value = 0
SE = 0.00476
Z = 1.68
p= 0.9535
0.0465 < 0.05
Reject the null hypothesis
###b.
Type 1 Error reject the null hypothesis when is actaully true.

##4.16.
###a.
Parameter of interest: the mean hours of all working Americans
point estimate: 41.8-49.4 =2.4
###b.
Independence between groups, normally distributed, and independence between individuals. Conditions are met
###c.
H0: mean1 - mean2 =0
HA: mean1 does not equal mean2
SE= 0.894
T = 2.684
df= 504
p less than 0.010 for a two tail test 0.005 for a one tail test.
smaller than 0.05 so we reject the null hypothesis
###d.
Those will college degrees might have jobs that are more challenging and thus require more time.

##5.10
###a.
Slight positive coorlation.
###b.
Strong positive linear coorlation
###c.
Diameter because the residuals are closer to 1 and there is a stronger coorlation.

#PART 2
##1.
```{r}
download.file("http://www.openintro.org/stat/data/ames.RData", destfile = "ames.RData")
load("ames.RDATA")
price <- ames$SalePrice
samp1 <- sample(price, 60)
pe <- mean(samp1)
pe
samp_mean <- mean(samp1)
```
##2.
```{r}
samp_mean <- rep(NA, 50)
samp_sd <- rep(NA, 50)
for(i in 1:50){
samp <- sample(price, 60)
samp_mean[i] <- mean(samp) 
samp_sd[i] <- sd(samp)
}
hist(samp_mean)
```
##3. 
```{r}
lower_vector <- samp_mean - 1.96 * samp_sd / sqrt(60)
upper_vector <- samp_mean + 1.96 * samp_sd / sqrt(60)
c(lower_vector[1], upper_vector[1])
plot_ci(lower_vector, upper_vector, mean(price))
```

0.88 of confidence intervals include the true population mean. This less than the confidence interval of 95%. Possibly this is due to the small sample size which can effect the standard Error.

##4.
```{r}
lower_vector <- samp_mean - 2.58 * samp_sd / sqrt(60)
upper_vector <- samp_mean + 2.58 * samp_sd / sqrt(60)
c(lower_vector, upper_vector)
plot_ci(lower_vector, upper_vector, mean(price))
```
For a 99% confidence interval, the critical value is 2.58

##5.
```{r}
lower_vector <- samp_mean - 2.58 * samp_sd / sqrt(60)
upper_vector <- samp_mean + 2.58 * samp_sd / sqrt(60)
c(lower_vector[1], upper_vector[1])
plot_ci(lower_vector, upper_vector, mean(price))
df <- data.frame(lower_vector = lower_vector, upper_vector = upper_vector)
+nrow(subset(df, lower_vector < mean(ames$SalePrice) & upper_vector > mean(ames$SalePrice))) / length(sample_means60)
```

This creates a confidence interval of 98%, and only one confidence interval does not include the mean.